\chapter{Testing}
Describe your Test Plan -- how the program or system
was verified. Put the actual test results in an Appendix
if they are repetitive but relevant. Detailed test data
may be omitted from the report if not relevant,
however an accurate summary of tests should be
included in the Report itself. Sometimes non-working
designs are described in project reports as though
they work, when in reality they don’t, or only partially
work. Therefore a precise description of what works
and how this has been established is important.
Examiners may try to compile, use, or test
deliverables themselves (even after your report is
submitted), and your report should accurately reflect
the state of the project.
This section is normally useful for software or
hardware deliverables and less relevant in analytical
projects.

\chapter{Results}
This covers an area different from the 'Testing'
chapter, and relates to the understanding and analysis
of the algorithm, program, or hardware behaviour.
Where the deliverable is a product with easily
quantified performance then the previous Chapter
shows how functional correctness is established,
while this Chapter shows qualitatively or
quantitatively how well the product works. The list
below shows typical content, not all of this will be
applicable to all projects.
- An empirical relationship between
parameters and results may be investigated,
typically through the use of appropriate
graphs.
- Where theory predicts aspects of
performance the results can be compared 
TJWC Final Year Projects 4
with expectation and differences noted and (if
possible) explained.
- Semi-empirical models of behaviour may be
developed, justified, and tested.
- The types of experiments/simulations that
were carried out should be described. Why
were certain experiments carried out but not
others? What were the important parameters
in the simulation and how did they affect the
results? If there are very many graphs and
tables associated with this chapter they may
be put in the Appendix, but it is generally
better to keep these close to the text they
illustrate, as this is easier for the reader.

\section{Needing to use one-hot encoding}
\section{Initial results with Taxi2 and original state decomposition algorithm}
\section{Effect of different encoding methods}
\section{Effect of different number of parameters}
\section{Effect of using reduced encoding (taking advantage of state decomposition for smaller input vector)}
\section{Performance gain of DeltaSwitch}
\section{Samples plots}
\section{Effect of wall / no wall}
\section{Effect of decomposing by destination or by position}
\section{Techniques to learn switch and relationship with transfer learning + fair comparison}

\input{evaluation_plan.tex}